\chapter{Simulations}
\label{chap:Simulations}

To better grasp the effects of $Q\to I$ leakage into the 21cm signal, we generate several
random realizations of the sky, each consisting of many polarized point sources. Each source passes
through a Faraday screen with some rotation measure, chosen from a distribution based on current
measurements. Next, we simulate that source for a single baseline. Finally, we calculate the power
spectrum measured by that visibility. Only one visibility needs to be simulated, because the
delay-spectrum approach makes use of the fact that each baseline measures the 21cm EoR with a range
of $k$-modes determened by the baseline length, orientation, and bandwidth.

Rather than creating an exact simulation of the physical sky, we create a simulation whose
statistical properties are physically motivated. This choice reflects a desire for simple, easliy
tunable parameters for the simulation. In that same spirit, we model all sources simply as point
sources with a Poisson angular distribution. The simulation's primary concern  with the spectral information
of polarized foregrounds allows us to justify neglecting the angular terms. This is equivalent to
assuming for all the relevant $k$-modes, $k_{||} \gg k_{\perp}$. Emphasis on the $k_{||}$, or
line-of-sight, spectral modes also motivates our decision to model the sky as nuemerous point
sources. For a more detailed discussion of diffuse polarized emission, we direct the reader to
\citet{Jelic2010}.

\input{Pspec/Simulations/Parameters}
\input{Pspec/Simulations/PowerSpectra}
\input{Pspec/Simulations/ConsistencyChecks}
\input{Pspec/Simulations/Mitigation}
