% Thesis Acknowledgements ------------------------------------------------

\begin{acknowledgements}


  Without the help and work of an immense number of people, this thesis would never have been
  made. I know most theses in physics say this, but it's true: I have a new appreciation of 
  the phrase ``standing on the shoulders of giants'' from having worked with you all.

  A very incomplete list of specfic thank you's:

  The PAPER Team --- I feel lucky to have worked alongside each one of you. To the guys who
  designed the instrument, Rich and the digital team at UCB in particular, I'm in awe. For PAPER to be 
  as stable and reliable as it is --- what an impressive feat! To everyone who went on deployments
  with me, it's been a pleasure getting to know you, and I'll miss working with you guys. William, 
  thank you in particular for making South Africa such a friendly and hospitable place for me.  

  Aaron --- So much of this thesis builds on your ideas, and I've learned so much from you. If there
  were one person without whom none of this would have happend, it would be you.
    
  Danny --- You've been such a close comrade through this whole process. Thank you for answering my
  dumb questions, for listening to me gripe, for helping me bang my head against code, and for
  getting me through my ``natural enmity with computers,'' as you called it. I have no words...

  James --- Thank you for giving me the freedom I've needed to get here: for putting me in
  uncomfortable situations that have allowed me to grow (who would have thought that I could build a
  working computer cluster!), for giving me the resources to learn and grow as a student and as a
  scientist, and for linking me to such a large network of people from whom I've learned so much. 

  My Parents --- Y'all are a constant source of unquestioning support. Especially in the last year,
  this has been crucial to my mental health, and to helping me find the gumption to finish this. In
  many ways, this thesis is yours, because without the twenty-some-odd years of hard work and
  encouragement you've given me, I'd never have made it this far. I'm lucky to have you guys.

  Lucia --- If there is a hero to my epic of reionization, it's you. I don't think I could ever
  write enough to thank you for how much you've given me throughout this whole ordeal. I think the
  best show of gratitude I could give you is a promise never to get another Ph.D. I love you more
  than words can say, and I don't even want to think about where I'd be right now if it weren't 
  for you. 
  
  To show gratitude to, and to indicate the involvement of everyone who contributed to the
  making of this thesis, I'll always use the word ``we'' when referring to the authors of 
  this thesis. I'll try only to break from this convention in footnotes and other comments
  from the peanut gallery.  

\end{acknowledgements}

% ------------------------------------------------------------------------


